---
title: "sarthyp_behaviour"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(cowplot)
library(tidyverse)
```

## SARTHYP Behaviour Analysis
 - SART task behaviour
 - responses to thought probes
 - we will look at the difference Hypno-Norm for each type of probe /response


```{r, echo=FALSE}
# load data
data <- read.csv("/media/guakamole/NAS-DATA/SARTHYP Data/Analyse_behavior/all_events_R_dataframe.csv",header=T)
data$Subject <- factor(data$Subject)
```



## 1D scatterplots = stripcharts of differences between Norm and Hypno for each group

```{r, echo=FALSE}
# compute the Norm - Hypno difference score for each response for each participants
diff_cond <- data %>%
  group_by(Subject, Group, Type) %>%
  summarize(
    count=n(),
    diff = (Total[Session=="hypno"] - Total[Session=="norm"])
  )

# plot scatterplot per group


value <- diff_cond$diff
participant <-diff_cond$Subject[diff_cond$Type=="MW"] 
resp <- diff_cond$Type[diff_cond$Group=="low"] 
diff <- data.frame(participant, resp, value)

#get only thought probes
probes<-subset(diff, ! resp %in% c("Go", "NoGo", "Missed Go", "Miss NoGo" ), drop = TRUE)

set.seed(8)
diffstrip <- ggplot(probes, aes(x=resp, y=value, fill=resp, colour=resp, shape=resp)) +
  geom_abline(intercept = 0, slope = 0) +
  geom_jitter(position=position_jitter(0.4), size=2, stroke=0.5) +
  
  labs(title="Differences: Hypnosis - Normal") 
diffstrip
```
## There is not much difference between normal and hypnosis 



```{r, echo=FALSE}
#get only behaviour
behav<-subset(diff, ! resp %in% c("Focus", "MW", "Sensory", "Related Thought" ), drop = TRUE)

set.seed(8)
diffstrip <- ggplot(behav, aes(x=resp, y=value, fill=resp, colour=resp, shape=resp)) +
  geom_abline(intercept = 0, slope = 0) +
  geom_jitter(position=position_jitter(0.4), size=2, stroke=0.5) +
  
  labs(title="Differences: Hypnosis - Normal") 
diffstrip


```

## There is not much difference between normal and hypnosis...

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
